Project 4

### 2018-11-19 Project4/report/ms.tex

The two-dimensional binary Ising model has analytical expectation values. The partition function
%
\begin{equation*}
    z = \sum_i \Omega(E_i) e^{\beta E_i},
\end{equation*}
%
where $\Omega(E_i)$ is the degeneracy of energy $E_i$ and $\beta = 1/k_BT$. From Table \ref{tab:energies} we can see that there are 2 energies that are non-zero: $\pm 8J$, which both has a degeneracy of 2. The energy equal to zero has a degeneracy of 12. Expanding the sum of the partition function we get 
%
\begin{align*}
    z &= 2e^{8J\beta} + 12 + 2e^{-8J\beta} \\
    &= 12 + 2\left(e^{8J\beta} + e^{-8J\beta}\right),
\end{align*}
%
where we have inserted $e^0 = 1$. We know that $\cosh(x) = \frac{1}{2}\left( e^{-x} + e^x\right)$, inserting this gives
%
\begin{gather}\label{eq:z}
    Z = 12 + 4\cosh(8J\beta).
\end{gather}
%
The mean value of the energy is given by
%
\begin{align*}
    \langle E \rangle = -\frac{\partial }{\partial \beta} \ln Z = -\frac{1}{Z}\frac{\partial Z}{\partial \beta},
\end{align*}
%
which is found by inserting the partition function.
%
\begin{align*}
    \langle E \rangle &= -\frac{1}{Z}\frac{\partial}{\partial \beta} \left(12 + 4 \cosh\left(8J\beta\right)\right)\\
    &= -\frac{4}{Z}\left(8J\sinh\left(8J\beta\right)\right),
\end{align*}
pulling a factor 4 from the partition function and inserting we are left with a analytical solution to the mean energy of the lattice
%
\begin{gather*}
    \langle E \rangle = -\frac{8J\sinh\left(8J\beta\right)}{3 + \cosh(8J\beta}.
\end{gather*}
%
The heat capacity can be found by
%
\begin{align*}
    C_V &= \frac{1}{kT^2}\frac{\partial^2}{\partial \beta^2} \ln Z = \frac{1}{kT^2}\frac{\partial}{\partial \beta}\left(\frac{\partial}{\partial \beta} \ln Z\right),
\end{align*}
%
where we recognize the partial derivative in the parenthesis as the negative mean energy. 
%
\begin{align*}
    C_V = \frac{1}{kT^2}&\left(\frac{64J^2\cosh\left(8J\beta\right)\left(3 + \cosh\left(8J\beta\right)\right)}{\left(3 + \cosh\left(8J\beta\right)\right)^2}\right \\
    &-\left \frac{64J^2\sinh^2\left(8J\beta\right)}{\left(3 + \cosh\left(8J\beta\right)\right)^2}\right),
\end{align*}
%
by inserting for the mean energy and using the product rule. Further simplifications gives the mean heat capacity
%
\begin{gather*}
    C_V = \frac{1}{kT^2}\frac{64\cosh\left(8J\beta\right)}{ 3 + \cosh\left(8J\beta\right)}.
\end{gather*}
The susceptibility is given as
%
\begin{equation*}
    \chi = \frac{1}{kT}\left(\langle M^2 \rangle - \langle M \rangle^2\right).
\end{equation*}
%
To find the susceptibility of the system we consider the mean magnetic moment
%
\begin{equation*}
    \langle M \rangle = \frac{1}{Z} \sum_i |M_i| e^{-\beta E_i},
\end{equation*}
where we find the magnetic moment for a given energy in Table \ref{tab:energies}. So the mean magnetic moment is
%
\begin{equation*}
    \langle M \rangle = \frac{1}{Z}\left(4e^{8J\beta} + 4\left(2e^{0}\right) + 4\left(-2e^0\right) + -4e^{8J\beta} \right) = 0.
\end{equation*}
%
Further we calculate the mean of the  magnetic moment squared
%
\begin{equation*}
    \langle M^2 \rangle = \frac{1}{Z}\sum_i M_i^2 e^{-\beta E_i},
\end{equation*}
and again referring to Table \ref{tab:energies} we get
%
\begin{align*}
    \langle M^2 \rangle &= \frac{1}{Z}\left(16\left(2e^{8J\beta}\right) + 16\left(2e^0\right) \right) \\
    &= \frac{8\left(e^{8J\beta} + 1\right)}{3 + \cosh\left(8J\beta\right)}.
\end{align*}
So the susceptibility of the system is given as
%
\begin{equation*}
    \chi = \frac{1}{kT^2}\langle M^2 \rangle = \frac{1}{kT^2}\frac{8\left(e^{8J\beta} + 1\right)}{3 + \cosh\left(8J\beta\right)}
\end{equation*}
%
Further we find the mean of the absolute value of the magnetic moment by

\begin{align*}
    \langle |M| \rangle &= \frac{1}{Z} \sum_i |M_i| e^{-\beta E_i} \\
     &= \frac{1}{Z}\left(4e^{8J\beta} + 4\left(2e^{0}\right) + 4\left(|-2|e^0\right) + |-4|e^{8J\beta} \right) \\
     &= \frac{2e^{8J\beta} + 4}{3 + \cosh\left(8J\beta\right)},
\end{align*}
%
after pulling out a factor 4 from the partition function. To summarize we have the following analytical expression for the system
%
\begin{align*}
    \langle E \rangle &= -\frac{4}{Z}\left(8J\sinh\left(8J\beta\right)\right), \\
    \langle |M| \rangle &= \frac{2e^{8J\beta} + 4}{3 + \cosh\left(8J\beta\right)}, \\
    C_V &= \frac{1}{kT^2}\frac{64\cosh\left(8J\beta\right)}{ 3 + \cosh\left(8J\beta\right)}, \\
    \chi &= \frac{1}{kT^2}\frac{8\left(e^{8J\beta} + 1\right)}{3 + \cosh\left(8J\beta\right)}.
\end{align*}

@@

\begin{figure}[t]
\subfloat[Energy pr. spin.]{
  \includegraphics[width=9cm]{EofMCC-GS-T1-L20-1e5.pdf}
  \label{fig:L20-GS-E-T1}}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{
  \includegraphics[width=9cm]{MofMCC-GS-T1-L20-1e5.pdf}
  \label{fig:evaluation:L20-GS-M-T1}}
\caption{Time evolution (MC cycles) of energy and magnetic moment of an ordered initial state with temperature 1 kT/J. $10^5$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[t]
\subfloat[Energy pr. spin.]{%
  \includegraphics[width=8.65cm]{EofMCC-GS-T2_4-L20-1e5.pdf}
  \label{fig:L20-GS-E-T2.4}}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{
  \includegraphics[width=8.65cm]{MofMCC-GS-T2_4-L20-1e5.pdf}
  \label{fig:L20-GS-M-T2.4}}
\caption{Time evolution of energy and magnetic moment of an ordered initial state with temperature 2.4 kT/J. $10^5$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[t]
\subfloat[Energy pr. spin.]{%
  \includegraphics[width=8.65cm]{EofMCC-T1-L20-1e6.pdf}%
  \label{fig:L20-E-T1}%
}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{%
  \includegraphics[width=8.65cm]{MofMCC-T1-L20-1e6.pdf}%
  \label{fig:L20-M-T1}%
}
\caption{Time evolution of energy and magnetic moment of an random initial state with temperature 1 kT/J. $10^6$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[t]
\subfloat[Energy pr. spin.]{
  \includegraphics[width=8.65cm]{EofMCC-T2_4-L20-1e6.pdf}
  \label{fig:evaluation:revenue}}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{
  \includegraphics[width=8.65cm]{MofMCC-T2_4-L20-1e6.pdf}
  \label{fig:evaluation:avgPrice}}
\caption{Time evolution (MC cycles) of energy and magnetic moment of an random initial state with temperature 2.4 kT/J. $10^6$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=accepts_of_T-T1T2_4-L20.pdf,width=\linewidth,clip=}}
\caption{Logarithm of the accepted states as a function of the temperature for different number of Monte Carlo cycles. The left four dots corresponds to $T=1$ kT/J, and the right four dots corresponds to $T=2.4$ kT/J. The initial spins are randomly organized.}
\label{fig:logAccepts(t)}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=accepts-T1T2_4-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{Logarithmic plot of accepted states as a function of }
\label{fig:logAccepts}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=CV-T2-23.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=CV-T2-23.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=CV-T22-24.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=E-T2-23.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=E-T22-24.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=FittedTc.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=M-T2-23.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=M-T22-24.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=PE-T1-L20-1e6.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=PE-T2_4-L20-1e6.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=X-T2-23.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=X-T22-24.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

@@

%\begin{figure}[t]
%
%\mbox{\epsfig{figure=filename.eps,width=\linewidth,clip=}}
%
%\caption{Description of figure -- explain all elements, but do not
%draw conclusions here.}
%\label{fig:figure_label}
%\end{figure}

>>>>

The two-dimensional binary Ising model has analytical expectation values. The partition function
%
\begin{equation*}
    z = \sum_i \Omega(E_i) e^{\beta E_i},
\end{equation*}
%
where $\Omega(E_i)$ is the degeneracy of energy $E_i$ and $\beta = 1/k_BT$. From Table \ref{tab:energies} we can see that there are 2 energies that are non-zero: $\pm 8J$, which both has a degeneracy of 2. The energy equal to zero has a degeneracy of 12. Expanding the sum of the partition function we get 
%
\begin{align*}
    z &= 2e^{8J\beta} + 12 + 2e^{-8J\beta} \\
    &= 12 + 2\left(e^{8J\beta} + e^{-8J\beta}\right),
\end{align*}
%
where we have inserted $e^0 = 1$. We know that $\cosh(x) = \frac{1}{2}\left( e^{-x} + e^x\right)$, inserting this gives
%
\begin{gather}\label{eq:z}
    Z = 12 + 4\cosh(8J\beta).
\end{gather}
%
The mean value of the energy is given by
%
\begin{align*}
    \langle E \rangle = -\frac{\partial }{\partial \beta} \ln Z = -\frac{1}{Z}\frac{\partial Z}{\partial \beta},
\end{align*}
%
which is found by inserting the partition function.
%
\begin{align*}
    \langle E \rangle &= -\frac{1}{Z}\frac{\partial}{\partial \beta} \left(12 + 4 \cosh\left(8J\beta\right)\right)\\
    &= -\frac{4}{Z}\left(8J\sinh\left(8J\beta\right)\right),
\end{align*}
pulling a factor 4 from the partition function and inserting we are left with a analytical solution to the mean energy of the lattice
%
\begin{gather*}
    \langle E \rangle = -\frac{8J\sinh\left(8J\beta\right)}{3 + \cosh(8J\beta}.
\end{gather*}
%
The heat capacity can be found by
%
\begin{align*}
    C_V &= \frac{1}{kT^2}\frac{\partial^2}{\partial \beta^2} \ln Z = \frac{1}{kT^2}\frac{\partial}{\partial \beta}\left(\frac{\partial}{\partial \beta} \ln Z\right),
\end{align*}
%
where we recognize the partial derivative in the parenthesis as the negative mean energy. 
%
\begin{align*}
    C_V = \frac{1}{kT^2}&\left(\frac{64J^2\cosh\left(8J\beta\right)\left(3 + \cosh\left(8J\beta\right)\right)}{\left(3 + \cosh\left(8J\beta\right)\right)^2}\right \\
    &-\left \frac{64J^2\sinh^2\left(8J\beta\right)}{\left(3 + \cosh\left(8J\beta\right)\right)^2}\right),
\end{align*}
%
by inserting for the mean energy and using the product rule. Further simplifications gives the mean heat capacity
%
\begin{gather*}
    C_V = \frac{64J^2}{k_B T^2} \left(\frac{\cosh(8\beta J)(3+\cosh(8 \beta J)) - \sinh^2(8\beta J)}{\left(3 + \cosh(8\beta J)\right)^2}\right)
\end{gather*}
The susceptibility is given as
%
\begin{equation*}
    \chi = \frac{1}{kT}\left(\langle M^2 \rangle - \langle M \rangle^2\right).
\end{equation*}
%
To find the susceptibility of the system we consider the mean magnetic moment
%
\begin{equation*}
    \langle M \rangle = \frac{1}{Z} \sum_i |M_i| e^{-\beta E_i},
\end{equation*}
where we find the magnetic moment for a given energy in Table \ref{tab:energies}. So the mean magnetic moment is
%
\begin{equation*}
    \langle M \rangle = \frac{1}{Z}\left(4e^{8J\beta} + 4\left(2e^{0}\right) + 4\left(-2e^0\right) + -4e^{8J\beta} \right) = 0.
\end{equation*}
%
Further we calculate the mean of the  magnetic moment squared
%
\begin{equation*}
    \langle M^2 \rangle = \frac{1}{Z}\sum_i M_i^2 e^{-\beta E_i},
\end{equation*}
and again referring to Table \ref{tab:energies} we get
%
\begin{align*}
    \langle M^2 \rangle &= \frac{1}{Z}\left(16\left(2e^{8J\beta}\right) + 16\left(2e^0\right) \right) \\
    &= \frac{8\left(e^{8J\beta} + 1\right)}{3 + \cosh\left(8J\beta\right)}.
\end{align*}
So the susceptibility of the system is given as
%
\begin{equation*}
    \chi = \frac{1}{kT^2}\langle M^2 \rangle = \frac{1}{kT^2}\frac{8\left(e^{8J\beta} + 1\right)}{3 + \cosh\left(8J\beta\right)}
\end{equation*}
%
Further we find the mean of the absolute value of the magnetic moment by

\begin{align*}
    \langle |M| \rangle &= \frac{1}{Z} \sum_i |M_i| e^{-\beta E_i} \\
     &= \frac{1}{Z}\left(4e^{8J\beta} + 4\left(2e^{0}\right) + 4\left(|-2|e^0\right) + |-4|e^{8J\beta} \right) \\
     &= \frac{2e^{8J\beta} + 4}{3 + \cosh\left(8J\beta\right)},
\end{align*}
%
after pulling out a factor 4 from the partition function. To summarize we have the following analytical expression for the system
%
\begin{align*}
    &\langle E \rangle = -\frac{4}{Z}\left(8J\sinh\left(8J\beta\right)\right), \\
    &\langle |M| \rangle = \frac{2e^{8J\beta} + 4}{3 + \cosh\left(8J\beta\right)}, \\
    &C_V = \frac{64J^2}{k T^2} \left(\frac{\cosh(8\beta J)(3+\cosh(8 \beta J)) - \sinh^2(8\beta J)}{\left(3 + \cosh(8\beta J)\right)^2}\right), \\
    &\chi = \frac{1}{kT^2}\frac{8\left(e^{8J\beta} + 1\right)}{3 + \cosh\left(8J\beta\right)}.
\end{align*}

@@

\begin{deluxetable}{lccccc}
\tablewidth{0pt}
\tablecaption{\label{tab:analytical}}
\tablecomments{Comparison of analytical and numerical results for various values.}
\tablecolumns{4}
\tablehead{ $\langle E \rangle$ & $\langle |M| \rangle$ & $C_V$ & $\chi$}
\startdata
-7.983 & 3.994 & 0.128 & 15.973 
\enddata
\end{deluxetable}

\begin{deluxetable}{lccccc}
\tablewidth{0pt}
\tablecaption{\label{tab:results}}
\tablecomments{Comparison of analytical and numerical results for various MC cycles. Lattice size is 2x2, temperature 1 kT/J and initial spin randomly set.}
\tablecolumns{5}
\tablehead{MC cycles & $\langle E \rangle$ & $\langle |M| \rangle$ & $C_V$ & $\chi$}
\startdata
1e3 & -7.976 & 3.992 & 0.191 & 0.023 \\
5e3 & -7.984 & 3.994 & 0.127 & 0.027 \\
1e4 & -7.968 & 3.989 & 0.254 & 15.928 \\
1e5 & -7.984 & 3.994 & 0.122 & 15.403 \\
1e6 & -7.984 & 3.994 & 0.127 & 15.973 \\
Analytical & -7.983 & 3.994 & 0.128 & 15.973 
\enddata
\end{deluxetable}

\begin{figure}[h]
\subfloat[Energy pr. spin.]{
  \includegraphics[width=9cm]{EofMCC-GS-T1-L20-1e5.pdf}
  \label{fig:L20-GS-E-T1}}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{
  \includegraphics[width=9cm]{MofMCC-GS-T1-L20-1e5.pdf}
  \label{fig:evaluation:L20-GS-M-T1}}
\caption{Time evolution (MC cycles) of energy and magnetic moment of an ordered initial state with temperature 1 kT/J. $10^5$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[h]
\subfloat[Energy pr. spin.]{%
  \includegraphics[width=8.65cm]{EofMCC-GS-T2_4-L20-1e5.pdf}
  \label{fig:L20-GS-E-T2.4}}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{
  \includegraphics[width=8.65cm]{MofMCC-GS-T2_4-L20-1e5.pdf}
  \label{fig:L20-GS-M-T2.4}}
\caption{Time evolution of energy and magnetic moment of an ordered initial state with temperature 2.4 kT/J. $10^5$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[h]
\subfloat[Energy pr. spin.]{%
  \includegraphics[width=8.65cm]{EofMCC-T1-L20-1e6.pdf}%
  \label{fig:L20-E-T1}%
}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{%
  \includegraphics[width=8.65cm]{MofMCC-T1-L20-1e6.pdf}%
  \label{fig:L20-M-T1}%
}
\caption{Time evolution of energy and magnetic moment of an random initial state with temperature 1 kT/J. $10^6$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[h]
\subfloat[Energy pr. spin.]{
  \includegraphics[width=8.65cm]{EofMCC-T2_4-L20-1e6.pdf}
  \label{fig:evaluation:revenue}}\\
\subfloat[Absolute value of the magnetic moment pr. spin.]{
  \includegraphics[width=8.65cm]{MofMCC-T2_4-L20-1e6.pdf}
  \label{fig:evaluation:avgPrice}}
\caption{Time evolution (MC cycles) of energy and magnetic moment of an random initial state with temperature 2.4 kT/J. $10^6$ Monte Carlo cycles.}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=accepts_of_T-T1T2_4-L20.pdf,width=\linewidth,clip=}}
\caption{Logarithm of the accepted states as a function of the temperature for different number of Monte Carlo cycles. The left four dots corresponds to $T=1$ kT/J, and the right four dots corresponds to $T=2.4$ kT/J. The initial spins are randomly organized.}
\label{fig:logAccepts(t)}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=accepts-T1T2_4-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{Logarithmic plot of accepted states as a function of Monte Carlo cycles. The initial spins are randomly organized.}
\label{fig:logAccepts}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=E-T2-23.pdf,width=\linewidth,clip=}}
\caption{Mean energy pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.03, making it ten steps.}
\label{fig:E-T2-23}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=M-T2-23.pdf,width=\linewidth,clip=}}
\caption{Mean absolute value of magnetic moment pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.03, making it ten steps.}
\label{fig:M-T2-23}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=CV-T2-23.pdf,width=\linewidth,clip=}}
\caption{Heat capacity pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.03, making it ten steps.}
\label{fig:CV-T2-23}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=X-T2-23.pdf,width=\linewidth,clip=}}
\caption{Susceptibility pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.03, making it ten steps.}
\label{fig:chi-T2-23}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=E-T22-24.pdf,width=\linewidth,clip=}}
\caption{Mean energy pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.01, making it twenty steps.}
\label{fig:E-T22-23}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=M-T22-24.pdf,width=\linewidth,clip=}}
\caption{Mean abslute value of the magnetic moment pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.01, making it twenty steps.}
\label{fig:M-T22-23}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=CV-T22-24.pdf,width=\linewidth,clip=}}
\caption{Heat capacity pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.01, making it twenty steps.}
\label{fig:CV-T22-24}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=X-T22-24.pdf,width=\linewidth,clip=}}
\caption{Susceptibility pr. spin for various amounts of MC cycles. Initial spin state is random. Temperature varies with a step size of 0.01, making it twenty steps.}
\label{fig:chi-T22-23}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=FittedTc.pdf,width=\linewidth,clip=}}
\caption{Linear regression used on the critical temperatures at points of 1/L for $L = 40$, $60$, $80$ and $100$ gives the function $y(x) = 3.45x + 2.22$.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=PE-T1-L20-1e6.pdf,width=\linewidth,clip=}}
\caption{Histogram of the probability as a function of energy. Temperature is 1 kT/J. Initial spin states are random.}
\label{fig:figure_label}
\end{figure}

\begin{figure}[h]
\mbox{\epsfig{figure=PE-T2_4-L20-1e6.pdf,width=\linewidth,clip=}}
\caption{Histogram of the probability as a function of energy. Temperature is 2.4 kT/J. Initial spin states are random.}
\label{fig:figure_label}
\end{figure}

\begin{deluxetable}{cccc}
\tablewidth{0pt}
\tablecaption{\label{tab:runtimes40}}
\tablecomments{Run times for a 40x40 lattice for $10^5$ Monte Carlo cycles. Temperature set to 1 kT/J and the initial state for the spins are random.}
\tablecolumns{4}
\tablehead{Run & 1 core & 4 core & Difference}
\startdata
1 & 13.910 & 4.448 & 9.461 \\
2 & 14.348 & 4.530 & 9.817 \\
3 & 14.407 & 4.636 & 9.770 \\
Average & 14.221 & 4.538 & 9.683
\enddata
\end{deluxetable}

\begin{deluxetable}{cccc}
\tablewidth{0pt}
\tablecaption{\label{tab:runtimes100}}
\tablecomments{Run times for a 100x100 lattice for $10^5$ Monte Carlo cycles. Temperature set to 1 kT/J and the initial state for the spins are random.}
\tablecolumns{5}
\tablehead{Run & 1 core & 4 core & Difference}
\startdata
1 & 91.137 & 34.434 & 62.702 \\
2 & 83.662 & 30.455 & 53.207 \\
3 & 86.905 & 28.534 & 58.371 \\
Average & 87.235 & 31.141 & 58.093
\enddata
\end{deluxetable}

@@

%\begin{figure}[h]
%
%\mbox{\epsfig{figure=filename.eps,width=\linewidth,clip=}}
%
%\caption{Description of figure -- explain all elements, but do not
%draw conclusions here.}
%\label{fig:figure_label}
%\end{figure}
